As described in Section~\ref{sec:2}, the heavy resonance predicted by many BSM play a key role in understanding many fundamental phenomena. The narrow heavy resonance which decays into two gluons final state at the LHC, appears to be two hadronic jets in the detector. Produced by the QCD processes, the dijet events have a smoothly falling distribution of the invariant mass \mjj, whereas two jets appear to be a resonance in the \mjj spectrum. As a result, searches for dijet resonance are one of the flagship exotics analyses in ATLAS.


Besides, on the assumption that the resonant sample can be classified according to the type of parton that initiated the jets, the sensitivity of searches for new resonance can be improved by identifying the types of partons through which the potentially new particle interact.  One of simplest examples of such tagging is gluon-tagging one or more of the jets. The jet tagging procedure based on the number of
charged tracks with transverse momentum \pt~above 500 GeV is described in Section.~\ref{sec:5}. The \mjj spectrum of background is estimated from the data, which is used for the search in three categories: inclusive, single-gluon, and double-gluon tagged dijet systems. The inclusive \mjj spectrum is thus considered as control region for quark/gluon studies.



This chapter describes searches for new heavy particles decay in dijet final state as originating from gluons or quarks, a technique of quark/gluon tagging is employed to enhance the sensitivity to the results. The search performed uses full Run 2 data at $\sqrt{s} = 13$ TeV, with higher integrated luminosity compared to previous one (Run 1), significantly improvements in the understanding of systematic uncertainties are expected. On the other hand,  cross section upper limits will be set if no significantly resonances are observed.

The simplified procedures in this analysis is performed as following: 
\begin{itemize}
	\item Search for high-mass resonances in the untagged (inclusive), single-gluon tagged,
	and two-gluon tagged categories with dijet events.
	\item If significant resonances are found, claim something interesting, else the upper limits are set. 
	\item Model independent upper-limits are set on resonance cross sections in
	inclusive, single-gluon tagged, and two-gluon tagged categories.
	\item For the specific resonance model, set lower limits on the relevant scales in inclusive, single-gluon tagged, and two-gluon tagged categories.
	dijet systems.
\end{itemize}

\subsection{Monte Carlo models}
\label{sec:benchmark_signals}.  % uncomment if label used. 
\input{Texfiles/02-benchmark_signals.tex}
\clearpage

\subsection{Events selections}
\label{sec:event_selection}
\input{Texfiles/03-event_selection.tex}
\clearpage


\subsection{Quark-Gluon Sample Selection}
\label{sec:QGselection}.  % uncomment if label used. 
\input{Texfiles/04-QGselection.tex}
\clearpage

\subsection{Signal Optimisation}
\label{sec:Optimisation} % uncomment if label used. 
\input{Texfiles/05-Optimisation.tex}
\clearpage

\subsection{Statistical Framework}
%\label{sec:statistical} % uncomment if label used. 
\input{Texfiles/06-StatisticalFramework.tex}
\clearpage


\subsection{Systematic uncertainties}
\input{Texfiles/systematics.tex}
\clearpage


\subsection{Results}
\input{Texfiles/09-Results.tex}
\clearpage

%\subsubsection{Search results}
%\label{sec:6.6.1}

%\subsubsection{Limit setting results}
%\label{sec:6.6.2}


